%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Cody}{Kinneer}
% \title{Curriculum Vitae}         % optional, remove / comment the line if not wanted
\address{10388 Circle East}{Meadville, PA 16335}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(724)~261~9615}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{kinneerc@allegheny.edu}                               % optional, remove / comment the line if not wanted
\homepage{kinneerc.github.io}                         % optional, remove / comment the line if not wanted
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{Anticipated 2012--2016}{Bachelor of Science in Computer Science}{Allegheny
College}{Meadville, PA}{\textit{3.790}/\textit{4.000}}{Minor: Political Science}  % arguments 3 to 6 can be left empty
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Undergraduate Thesis}
\cvitem{Title}{\emph{Query-aware Search-based Schema Testing}}
\cvitem{Supervisors}{Dr.\ Gregory M.\ Kapfhammer, Dr.\ Robert Roos}
\cvitem{Description}{The results of automated testing tools are often
difficult to interpret. The addition of query-awareness to test data generation
  allows the user to specify relational database queries to serve as
  tests, making it easier for the tester to find bugs in relational database schemas.}

  % Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{library}                        % 'publications' is the name of a BibTeX file

\section{Experience}
  \subsection{Research}

  \cventry{Summer 2015}{Cupper Scholar}{Allegheny
  College}{Meadville, PA}{}{Database testing, search-based test data
  generation, and performance evaluation\newline{}%
Detailed achievements:%
\begin{itemize}%
\item Developed technique for automated empirical analysis of test data
  generation tools.
\item Conducted a large-scale experiment using a high performance
  computer cluster.
\item Presented results at an international conference and gave a
  technical demonstration during poster session.
\end{itemize}}

  \cventry{Summer 2014}{National Science Foundation Research
  Experience for Undergraduates}{University of Colorado Colorado Springs}{Colorado
  Springs, CO}{}{Mobile application testing and machine learning\newline{}%
Detailed achievements:%
\begin{itemize}%
\item Studied behavior of Android applications and test suites using
  aspect-oriented programming.
\item Evaluated test suite adequacy by probabilistic comparison to user
  interactions.
\item Communicated research by writing reports and delivering
  presentations.
\end{itemize}}

\subsection{Teaching}
\cventry{Fall 2014--Present}{Computer Science Tutor}{Allegheny
College}{Meadville, PA}{}{Reinforce lab assignment content to computer science
students during weekly drop-in hours.}
\cventry{June 2015}{Instructor}{ILead PA, Professional
Conference}{Harrisburg, PA}{}{Taught an
interactive two hour class on embedded systems programming projects for libraries.}
\cventry{Spring 2014}{Freshman Seminar Teaching Assistant}{Allegheny
College}{Meadville, PA}{Dr.\ Howard Tamashiro}{Assisted transfer students with writing
skills and adapting to life at Allegheny College.}

\subsection{Vocational}
\cventry{2012--Present}{Information Technology Department}{Meadville Public
Library}{Meadville, PA}{}{Design and implement software, analyze data,
automate reports\newline{}%
Detailed achievements:%
\begin{itemize}%
  \item Integrated Adobe Content Server with library's online catalogue
    for a statewide ebook hosting project.
    \begin{itemize}
    \item{\url{http://catalog.paliberty.net/}}
    \end{itemize}
  \item Developed computer-vision gate counters for reporting library visitors.
  \item Analyzed public Wi-Fi usage of nine public libraries in Crawford
    County.
\end{itemize}%
}

\section{Skills}
  \cvdoubleitem{Languages: Experienced}{Java, \LaTeX, R}{Working knowledge}{Python, C, Perl}
  \cvitem{Software}{Git, Eclipse, Vim, Linux, Windows}

\section{Awards}
  \cvitem{Certificate of Appreciation}{From the PA
  Department of Education for contributing to ILead.}
  \cvitem{Alden Scholar}{(Dean's List) Fall 2012--Present.}
  \cvitem{Outstanding Junior Major}{Prize for the computer science
  junior major with the highest GPA.}

% \cvdoubleitem{Experienced}{Java,\latex,R}{category 4}{XXX, YYY, ZZZ}
% \cvdoubleitem{Working Knowledge}{C, perl, }{category 5}{XXX, YYY, ZZZ}
% \cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Software}
\cvitem{ExpOse}{Automatically conduct empirical performance evaluations.}
\cvlistitem{\url{https://github.com/kinneerc/ExpOse}}
\cvitem{cv-counter}{Track the number of visitors moving through a doorway
using computer vision.}
\cvlistitem{\url{https://github.com/kinneerc/cv-counter}}
\cvitem{giv-planner}{Uses Google APIs to plan college operated shuttle
van routes.}
\cvlistitem{\url{https://github.com/kinneerc/giv-planner}}


\section{Contact}
  \cvdoubleitem{Mobile}{+1 (724) 261
  9615}{Email}{\href{mailto:kinneerc@allegheny.edu}{\nolinkurl{kinneerc@allegheny.edu} }}
  \cvdoubleitem{Website}{\url{kinneerc.github.io}}{GitHub}{\url{github.com/kinneerc}}
  \cvdoubleitem{Twitter}{\href{https://twitter.com/cbkinneer}{@cbkinneer}}{LinkedIn}{\url{linkedin.com/in/kinneerc}}


% Publications from a BibTeX file using the multibib package
% \section{Publications}
% \nocitebook{expose,seke}
% \bibliographystylebook{plain}
% \bibliographybook{library}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

% \clearpage
% -----       letter       ---------------------------------------------------------
% recipient data
\recipient{The University of Sheffield}{Western Bank, Sheffield,\\South Yorkshire S10 2TN, United Kingdom}
\date{December 10, 2015}
% \opening{Dear Sir or Madam,}
% \closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

The ability to store and process large amounts of information has
brought great benefits to society.  This ``big data'' enabled scientists
to map the human genome, discover the Higgs boson, and manage international
commerce.   While collecting this data has brought many benefits to
society, it also comes with risks.  When critical systems such as air
traffic control rely on the quality of data, incorrect data can have
devastating consequences. As a computer science major, I am interested in ensuring that the
software systems that we depend on are reliable.

Since my sophomore year at Allegheny College, I have had the opportunity
to collaborate with Dr.\ Phil McMinn at the University of Sheffield, in
conjunction with my advisor Dr.\ Gregory Kapfhammer and their PhD student Chris Wright.
While I was analyzing the data from my experiments, I realized that I
was the first person in the world to know what the performance
trade-offs looked like for search-based test data generation for
database schemas. The excitement of discovery from this experience drove
me to participate in a summer research experience for undergraduates
(REU) program funded by the National Science Foundation. As part of this
program, I traveled to the University of Colorado at Colorado Springs to
use machine learning to evaluate the quality of test suites written for mobile applications. 

My research has resulted in published papers and released software. This
summer, I continued my collaboration with  Dr.\ McMinn, Dr.\ Kapfhammer
and Chris Wright, and presented our paper titled “Automatically
Evaluating the Efficiency of Search-based Test Data Generation for
Relational Database Schemas” at the 27th International Conference on
Software Engineering and Knowledge Engineering. Our software for
conducting automatic scalability experiments is available on GitHub.

This year I am continuing work in this broad area for my
undergraduate thesis, which focusses on generating test data for
database queries. I am also working on a continuation of our previous work
which we hope to submit to the ACM Journal of Experimental Algorithmics.

Upon graduating from Allegheny College, I would like to continue my education
in the UK with Dr.\ McMinn as the next step towards my long-term goal of
obtaining a PhD in computer science and pursuing a career as a research
scientist. 

\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
